\begin{thebibliography}{9999}%\enlargethispage{\baselineskip}
\bibitem[1]{Bonon} Bonton E. Gup, \textsl{The Basics of Investing}. Canada: John Wiley \& Sons, Inc., 1989.\\
\bibitem[2]{Dineen} Sean Dineen, \textsl{Probability Theory in Finance - A Mathematical Guide to the Black-Scholes Formula}. Rhode Island: American Mathematcal Society, 2000.\\
\bibitem[3]{Nison} Steve Nison, \textsl{Beyond Candlesticks - New Japanese Charting Techniques Revealed}. Canada: John Wiley \& Sons, Inc., 1994.\\
\bibitem[4]{Barbara} Barbara Rockafeller, \textsl{Technical Analysis for Dummies}. Canada: Wiley Publishing, Inc., 2004.\\
\bibitem[5]{Investopedia:CMF} "Chaikin Money Flow" in Investopedia. [Online]. Available: Investopedia Online, \mbox{}\hfill\url{http://murphymorris.com/school/doku.php?id=chart_school:technical_indicators:chaikin_money_flow_c}. [Accessed: February 20, 2010].\\
\bibitem[6]{Investopedia:StochasticOscillator} "Stochastic Oscillator," in Investopedia. [Online]. Available: Investopedia Online, \mbox{}\hfill\url{http://www.investopedia.com/terms/s/stochasticoscillator.asp}. [Accessed: February 20, 2010].\\
\bibitem[7]{McMillan} Lawrence G. McMillan, \textsl{Options as a Strategic Investment}. New York: Penguin Putnam, Inc., 2002.\\
\bibitem[8]{Wealth} Wealth Intelligence Academy, Inc. \textsl{Master Trader - Advanced Trading}. Florida: Wealth Intelligence Academy, Inc., 2007.\\
\bibitem[9]{Wikipedia:AccumulationDistributionIndex} "Accumulation/Distribution Index", in Wikipedia. [Online]. Available: Wikipedia Online, \mbox{}\hfill\url{http://en.wikipedia.org/wiki/Accumulation/distribution_index}. [Accessed: February 20, 2010].\\
\bibitem[10]{Wikipedia:MACD} "MACD," in Wikipedia. [Online]. Available: Wikipedia Online, \mbox{}\hfill\url{http://en.wikipedia.org/wiki/MACD}. [Accessed: February 20, 2010].\\
\bibitem[11]{Wikipedia:RSI} "Relative Strength Index", in Wikipedia. [Online]. Available: Wikipedia Online, \mbox{}\hfill\url{http://en.wikipedia.org/wiki/Relative_strength_index}. [Accessed: February 20, 2010].\\
\bibitem[12]{Wikipedia:WilliamsR} "Williams \%R", in Wikipedia. [Online]. Available: Wikipedia Online, \mbox{}\hfill\url{http://en.wikipedia.org/wiki/Williams_\%25R}. [Accessed: February 20, 2010].\\
\bibitem[13]{Vichas} Robert P. Vichas, \textsl{Handbook of Financial Mathematics and Tables}. London: Prentice-Hall International, Inc., 1979.\\
\bibitem[14]{SmallStocks:CMF} "Chaikin Money Flow," in SmallStocks. [Online]. Available: SmallStocks Online, \mbox{}\hfill\url{http://www.smallstocks.com.au/technical-analysis/chaikin-money-flow-cmf}. [Accessed: February 20, 2010].\\
\end{thebibliography}







